Supplementary Material

### 2023-04-21 response_letter.Rmd

\RC{- Figure 6, panel 1: I would simply call the last category “decision error”, not “numerical and decision error”, this is already implied and by labelling it so explicitly it almost sounds as if there also exist decision errors that are not also numerical errors}

We have made changes in this Figure following suggestions from another reviewer. Now, it is Figure 4 (see p. 16). As you can see, now this category is called only “Decision error” following your recommendation.

\RC{- Page 22, line 10; typo: “which is both inefficient and *an* error-prone task”
- Page 22, line 14: typo: “out” should be “our”
- Page 23, line 17: typo: “issued” should be “issues”}

Thanks for checking! Fixed.

\RC{I’m looking forward to seeing this manuscript in print.

Signed,
Michèle Nuijten}

Thanks again for your useful feedback, we really appreciate your help in improving the manuscript!

# Reviewer \#3

\RC{- I think the reporting of results in the abstract could be imrpoved. Currently it states that 52 reanlysis results showed a discrepancy larger than 5\% from the original results - I think that sounds far more concerning that it actually is given that there were very few 'decision errors' and the authors believe that the reproducibiltiy issues had "little or no effect" on the original conclusions. So I think its worth stating that in the abstract to avoid any miscommunications. The point at which the authors 'qualitative assessment' and the input from the original authors is also not clear in the abstract.}

We agree that this is something that deserves to be mentioned in the abstract. We have added two sentences to the abstract:

>Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses from different sources. Of these, in the first stage 52 showed a discrepancy larger than 5% in the main results, \textcolor{blue}{in 10 of them, this discrepancy was solved after fixing a coding error and in 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

\RC{- The use of "analytic reproduciblity", "process reproducibility", and "outcome reproducibility" seems inconsistent, overlapping, and overall pretty confusing. The title and abstract refer to "analytical reproducibility", but the introduction focuses on  "process reproducibility" and "outcome reproducibility" (analytic reproducibility is not mentioned). Process reproducibility seems to be equated with data availability (or lack of), but I think it was originally intended to refer to all aspects of the analytic pipeline (original data + original code + original software environment, etc). This results in setences like "Based on the availability of primary data, either retrieved directly from the paper or upon request, 146 meta-analyses (67\%, see Fig. 3a) were labelled as process reproducible" This seems odd to me - because some of the cases labelled as "process reproducible" because the data were available, were in fact not reproducible when the authors tried to repeat the analyses. To be fair, I don't think the original sources of these terms defined them particularly helpfully, but I think the onus is on the authors to be clear about what they mean, and how they relate to each other in the present manuscript. For what its worth, I'd recommend just using "analytic reproducibility" to refer to the entire process of trying to repeat the original analyses with the original data to see if you get the same outcome (this seems an accurate description of what the authors did). If this process fails, identify the reason (if possible) which could be an early stage failure (e.g., lack of access to data or code) or a later stage failure (e.g.,  typo in original manuscript). Adding the terms "process reproducibility" and "outcome reproducibility" into the mix seems unnecessary and confusing to me.}

We see your point and agree that consistency in this matter should be improved. Indeed, as you rightly pointed out, in our study process-reproducibility is equated with data availability. As we see it, this is due to our design and the stage of the meta-analysis pipeline we focused on, not to concept itself. So, in our study it’s just a nomenclature matter.

However, we believe this distinction between process/outcome reproducibility is useful for the organization of the previous (and future) literature on meta-analysis reproducibility (as we did in Figure 1). For instance, this distinction allows us to classify studies that review the availability of required elements to reproduce a search strategy of a meta-analysis (e.g., Koffel & Rethlefsen, 2016) in a different category than those that verify the reproduction of the electronic search result (databases output) using those elements.

Regarding the organization of our own results, there would be no difference other than the label used. Therefore, we think it is a good idea to keep those labels for consistency with the terms and literature mentioned in the introduction.

We completely agree that the general consistency on this matter should be improved. To this end, we have clarified the synonymy between process-reproducibility and data-availability in our manuscript, and have made the following changes in the manuscript:

We have changed “analytical reproducibility” to “reproducibility” throughout the manuscript (also in the title and abstract) to avoid confusion and we have highlighted in the introduction (see p. 5) that:

>Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage. \textcolor{blue}{In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.}

We have also restructured the reproducibility success scheme (see p. 11):

>Each meta-analysis was labelled using the following \textcolor{blue}{two-level}^[This hierarchy is a minor deviation from the pre-registered protocol. It is essentially the same and the results are identical. It was introduced to improve clarity.] reproducibility success scheme. \textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible. In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt. In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.]. \textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.

Furthermore, in both figures (Figure 3 and new Figure 4) that display results and mention process reproducibility, data availability was also mentioned in brackets to avoid confusion.

\RC{- In the abstract: "From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology" - should say "clinical psychology" I think?}

Indeed. Thanks, fixed.

\RC{- Throughout the manuscript there is often reference to stages (e.g., "following the first stage of re-analysis") but I don't recall the different stages being clearly stated anywhere. Perhaps a flow digram would be helpful? I see Figure 6, but this appears to just be about the outcome reproducibility part of the study, and comes too late in the manuscript. This figure also doesn't include the authors "qualitative assessment" - its a bit unclear where that fits into the overall timeline.}

We have remade and moved (old) Figure 6 to a new Figure 4 in response to comments by the other reviewers. The current Figure 4 is a Sankey plot displaying the flow of the reproducibility attempts and it’s presented earlier in the manuscript (see p. 16). We hope that this figure at this place will be more informative about the stages we discuss.

\RC{- "The availability of necessary primary data was checked" - it would be helpful to precisely define "necessary" and "primary" here, especially in the context of meta-analysis. Its not clear to me whether primary means all the individual-unit data from the studies included in the meta-analyses or the summary effect sizes. And its not clear which data are considered necessary or unnecessary.}

We have modified the structure of this paragraph to begin by specifying the necessary data and at what level (see p. 8):

>## Retrieval of primary data
In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible...

\RC{- "confidential limits" - typo - "confidence"}

Thanks, fixed.

\RC{- Including "data reusability" in the title and abstract is superfluous given that reusing the data is a component of analytic reproducibiltiy and the authors did not try to reuse the data in any other way (the way its written implied to me that there would be some additional assessment of reusability).}

We agree that including “data reusability” could be redundant and, above all, misinterpreted as though some kind of additional reusability analysis had been done. Hence, we have removed it from title and abstract.

\RC{- Some parts of the methods section contain results (see e.g., bottom of page 8) and some parts of the results section contain commentary or opinion I would expect to be in the discussion section (e.g., "a remarkably low reponse rate").}

We have checked for this, and we have removed misplaced statements. Specifically, we have made the following changes:

-	Remove results on data types retrieved in each meta-analysis from Method section (p. 8)

-	Remove the rate of meta-analysis without analysis script code available from Method section (p. 9)

-	Remove “remarkably” from Results section (p. 15)

\RC{- Throughtout, it would be helpful if the numerator and denominator is provided as well as  percentages. The manuscript could be clearer about where the denominator comes from too. For example, "In 141 cases (97\%)" the denominator is presumably 145, but I'm not sure how we got there from the original 217 meta-analyses and I shouldn't have to do that calculation in my head. Another example is this sentence: "Only in 3% of the cases the primary data was retrieved upon request" - is that 3\% of all cases or 3\% of the cases in which data was requested?}

The two examples you mentioned are no longer in the current version. The first one was removed in the revision of results reported in method section (see previous comment). The second one was removed because it was indeed confusing. This 3% is of all cases. The rate of data retrieved from request out of the total of cases in which data was retrieved is not very informative of anything.

Furthermore, we have reviewed the text and added the numerator and denominator in cases where percentages are presented without enough context:

p. 14:

>Although attempts were made to retrieve data for 78 meta-analyses from 25 different papers by emailing the corresponding authors, data was only retrieved for 7 meta-analyses, from 3 different papers \textcolor{blue}{(12\%, 3/25, see Fig. 3c).} For the remaining 71 from 22 different papers, a reply providing some reasons not to share was received in \textcolor{blue}{32\% (8/25, see Fig. 3c)}, whereas no reply was received for the remainder of the meta-analyses.

p.15:

>Data \textcolor{blue}{were retrieved from} tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—\textcolor{blue}{in 92\% (134/146) of the cases.}

p. 18:

>\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos.

\RC{- Authors were contacted when data were not available, but it seems they were not asked for analysis scripts that were not available, was there a reason for this?}

Good point. There were some reasons for this:

-	Not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many used point and click software.

-	We expected script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis

-	We designed an approach to reconstruct the original analysis scheme .

We have mentioned those reasons in the revised manuscript (see p. 10):

>\textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}

\RC{- "Primary-level data and aggregate-level data described above were coded by five members of the group." - this is a bit unclear, it could that the data for each article were independely extracted five times (I dont think that's the intention).}

Thanks for spotting it. We have rephrased this as follows:

>\textcolor{blue}{Data collection procedure was carried out by five of the authors…}

\RC{- It would be interesting to get some sense of how important/influential the assessed meta-analyses are in order to gauge the impact of any reproducibility issues - perhaps include some descriptive data about citation counts?}

Great suggestion, thanks! We have added information on citation count of the papers included. See p. 12 and (new) Figure 2(c):

>\textcolor{blue}{...were cited 108.39 times on average (sd = 151.00; median = 57; interquartile range = 29-128; range = 3-1036)...}

\RC{- There are several sentences where I think its important to report the actual numbers rather than the authors verbal interpretation of the numbers e.g., "Data available in tables or forest plots shared in pdf or docx format –either in the document itself or in the supplementary materials– was found to be highly prevalent" and "This example of inconsistencies in original results was also found in other cases".}

We agree. We have added quantitative information on these cases:

p.15:

>Data \textcolor{blue}{were retrieved from} tables or forest plots in *pdf* or *docx* format—either in the document itself or in the supplementary materials—\textcolor{blue}{in 92\% (134/146) of the cases.}

p. 18:

>\textcolor{blue}{These examples of inconsistencies in original results or data were found in 4 cases (3\%, 4/146).} These appeared to be typos

\RC{- Figure 4 - the caption is cut off. Its difficult to make out error vs no error because of overlapping points, perhaps use colour here?}

Thank you for spotting it. With regards to the scatterplot, we have reduced the size of the crosses and added color to the Decision error label (see p. 18 and 19).

\RC{- "In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored. According to the authors, this link was not reported in the paper by mistake. The script was run on these data and the results were successfully reproduced." - Do the dates in the OSF archive indicate that the files were uploaded before the paper was published?}

Interesting point that we missed checking. It seems that the OSF repository was created just before the paper was accepted (02/06/2019 created, 13/06/2019 accepted). It seems that the OSF repo was created upon request of the journal. We think that this deserves to be mentioned in the manuscript, so we have added the following text (see p.21, footnote 7):

>\textcolor{blue}{According to the repository timeline the project was created on 02/06/2019 and according to the journal’s article history the paper was published on 13/06/2019. It seems that the repository was created as a journal requirement.}

\RC{- The authors responded "No" and "Not Applicable" to these prompts: "Does your paper rely on new or previously unpublished empirical data from your lab?", "If your paper presents new empirical work, does it include the following statement: “We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study”? It seems to me that both of these apply to the current manuscript (the nove empirical data is the results of the reproducibility assessments).}

We don’t know if it’s possible to modify the form. The most relevant point on your suggestion is related to include a statement about how we determine our sample size. We have included the following statement (see p. 8):

>Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified...\textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report. \textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

\RC{- I may have missed it, but it would be good to see data on when the target articles were published - a histogram in a supplement would do the job.}

Agree. We have added two panels to Figure 2 and one of them is a histogram of the publication year (see p. 13).

Thanks again for taking your time providing very useful feedback. We’re sure your suggestions have improved the manuscript.
